Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy

### 2020-01-23 manuscript/manuscript.Rmd
The Great Word Culling is done.

---
title: "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
  twitter: SuparnaChaudhry
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
  twitter: andrewheiss
date: "`r format(Sys.time(), '%B %e, %Y')`"
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: false
title-page: true
abstract: >-
  Government restrictions on NGOs have become increasingly pervasive across the globe. With reduced official aid and foundation funding available for NGOs, and an absence of philanthropic culture in many countries across the Global South, various NGOs are seeking funds from individual private donors in Western countries. How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making? While existing research has shown that donors rely on various heuristics from social networks and organizational-level attributes, we argue that domestic political environments of NGO host countries can also serve as an important structural-level heuristic that can influence donor behavior. Using a survey experiment, we find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad. We discuss the implications of our results on the sustainability of organizations working in repressive countries.
thanks: >-
  We thank Mark Buntaine, Michael DeCrescenzo, Jeffrey Friedman, Thomas Leeper, and Tristan Mahr for their helpful comments and input. We also thank Samantha Camilletti and Joshua Dutro for their excellent research assistance. This experiment received approval by the human subjects research committees at both Christopher Newport University (018.042) and Brigham Young University (E18104). We preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at <https://osf.io/dx973/>.
author-note: >-
  Suparna Chaudhry, PhD, Assistant Professor of Political Science, Christopher Newport University; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University. 
additional-info: Figures should appear in color online only, not in print.
correspondence: >-
  Correspondence concerning this article should be addressed to Suparna Chaudhry, PhD, Department of Political Science, Christopher Newport University, Newport News, VA 23606, 757-594-7821. Contact: suparna.chaudhry@cnu.edu
word-count: "4,081"
keywords: international NGOs, donor behavior, philanthropy, human rights, repression
---

@@

Following the 2011 Egyptian uprising, just as domestic non-governmental organizations (NGOs) began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy. Egypt is not alone in this endeavor-India, Bolivia, Hungary, Russia, and others have also imposed funding restrictions on NGOs [@Carothers:2015; @DPR:2015]. Consequently, official aid flows as well as grants from large foundations have considerably decreased to NGOs in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].

In response to this shift in the NGO funding landscape, organizations have increasingly turned to *foreign* individual donors to offset the loss of governmental and foundation funding [@BanksHulmeEdwards:2015]. This is because donations from *domestic* donors in repressive countries are unreliable and inconsistent. Citizens in the Global South often cannot support local NGOs, may prefer channeling funds to groups working on innocuous issues such as health and education over more contentious issues [@DPR:2015; @RPC:2016; @Brechenmacher:2017], or may be deterred by dismal tax incentives or a general fear of retribution [@HudsonInstitute:2015]. Therefore, NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy. This amount is not insignificant-by 2016, the amount directed towards civil society groups working in international affairs had increased to \$22.03 billion [@givingusa:2017].

In the face of increased crackdown on NGOs across the world, how do individual donors in the U.S. feel about donating to legally besieged NGOs abroad? Do legal restrictions on NGOs influence donors' decision to donate? Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974]. While much of this research has focused on heuristics from social networks and organizational practices [@CrosonShang:2011; @Tremblay-BoirePrakash:2017], in this research note, we argue that domestic political environments of NGO host countries can serve as one such structural heuristic that can also influence individual donor decisions. When donors are provided salient information about crackdown on NGOs and its impact on their activities, it can serve as a heuristic of organizational deservingness, and consequently influence donor preferences and behavior. We use a survey experiment to measure the effect of crackdowns on stated donor behavior and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs. This effect persists when mediated by other organizational-level heuristics like NGO issue area and its main funding sources.

@@

Below, we first summarize existing research on the determinants of philanthropic-giving to NGOs and lay out our expectations regarding how crackdowns on NGOs may affect charitable-giving. We then describe our survey and present the results. We conclude with implications for NGOs working in repressive countries and lay out questions ripe for future research.

@@

Substantial research on charitable-giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011], and more recently, the effect of social networks on philanthropy [@HerzogYang:2018]. However, research on individual donor behavior has overwhelming examined giving to local, rather than international causes. While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore private philanthropic giving because individuals rely on signals and heuristics that may differ from the benchmarks that large donors (whether official or private) rely on.

The decision to donate to an NGO is rarely rational. In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017]. Existing research shows that information on the efficiency of NGOs merely steers rather than encourages or discourages overall donations [@ryazanov:efficiency]. Similarly, the effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010; @SzperPrakash:2011]. Instead, donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming. These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].

In addition to the above factors that signal an NGO's trustworthiness and deservingness, we argue that structural factors—including whether an organization works abroad and the domestic political environment of the group's host country—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017]. We propose that the regulatory relationship between INGOs and their host governments serves as a signal of NGO trustworthiness and deservingness. NGO legislation is not inherently restrictive, and governments frequently use laws to regulate the behavior of NGOs [@BloodgoodTB; @DeMattee:2018]. Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy. These stricter anti-NGO laws can signal to donors that governments perceive these groups as threatening and may crack down on them.

We argue that donors perceive legal crackdowns differently from organizational-level heuristics—such as NGO missions, visions, values—because donors may be able to influence these latter attributes, at least to some extent. On the other hand, donors can do little to change the domestic political environment of another country. Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged NGOs, even if donors are not completely satisfied with some organizational-level features of a group. As such, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated.

@@

@fig:causal-path represents this relationship more formally. Legal crackdowns (**C**) have a direct effect on donor decisions (**Y**; donation likelihood and amount) because of their heuristic function. Legal crackdowns do not occur in isolation, however. Countries are more likely to repress NGOs both when organizational issue areas (**I**) are in tension with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015]. Both of these organizational characteristics thus confound the causal effect of crackdowns on donor decisions and must be accounted for in the analysis—issue areas and funding sources simultaneously influence the likelihood of crackdown while also serving as organizational heuristics that influence donor perceptions of NGO deservingness.

@@

The final heuristic that can influence individual donors that we examine is the *source of NGO funding*. Government grants to NGOs can often crowd out private funding for nonprofit organizations [@AndreoniPayne:2003; @Brooks:2000], though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991; @Heutel:2014]. Donors may feel less inclined to contribute to NGOs receiving funds from agencies like USAID because such funding can signal a lack of independence from the government. Organizations that receive substantial government funding frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012]. In contrast, individual donors who see that organizations are privately funded may feel that they can also contribute and help.

As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding again confounds the effect of anti-NGO crackdowns on donor behavior (see @fig:causal-path). As such, the combination of legal crackdown and funding may reshape donor perceptions of deservingness. Individual donors may be less likely to donate to government-funded NGOs that face restrictions, since legal trouble with the organization's primary funder could fuel private donor mistrust (i.e. perhaps the NGO did something to deserve crackdown). Donors thus may be likely to donate more to NGOs that rely on private funding.

@@

To measure the effect of structural and organizational-level heuristics on individual donor preferences, we use an experiment to vary the different signals donors are exposed to. Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs optimize and tailor their fundraising strategies for private individuals.

@@

We estimate the mean amount donated in each condition using a *t* distribution [@Kruschke:2013]:

@@

These results give partial support to H~3a~. The source of funding has little influence on the preferences to donate to humanitarian NGOs, but on average, donors are substantially more likely to want to give to privately-funded human rights NGOs than government-funded organizations. However, the effect of crackdowns reverses across conditions, as donors appear to both punish government-funded human rights NGOs that face legal difficulties and rally behind privately-funded NGOs facing those same hurdles. Respondents described their reasoning for the former as "[i]f the non-profit works in countries where non-profit activities are heavily restricted there's a good amount of waste and shortfalls in their activities and ability to assist others."[^3154467] Respondents also explained their motivation for increased support to privately funded NGOs as "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds.

@@

This trend also holds true when accounting for NGO issue area. The crackdown condition elicits higher donations for both the human rights and humanitarian NGOs, though with varying levels of significance (see @fig:amount-diffs(B–C)). Emphasizing legal crackdown increases donations to human rights NGOs by `r md_dollar(filter(amount, title == "Human rights")$mu_diff)`, but with a lower probability of significance (`r filter(amount, title == "Human rights")$p_neq0`). In contrast, crackdowns boost donations to humanitarian NGOs by `r md_dollar(filter(amount, title == "Humanitarian assistance")$mu_diff)`, a `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` increase beyond the control condition (`r filter(amount, title == "Humanitarian assistance")$p_neq0`). We thus find support for H~2b~: donors give more to besieged humanitarian NGOs. We also find evidence for H~3b~. Donors give `r md_dollar(filter(amount, title == "Private")$mu_diff)` more (a `r percent_0(filter(amount, title == "Private")$pct_change)` increase) to legally besieged NGOs that are privately funded (`r filter(amount, title == "Private")$p_neq0`), while the crackdown condition has little effect on the amount donated to government-funded NGOs (`r filter(amount, title == "Government")$p_neq0`).

Combining issue areas and funding sources adds more texture to these results. We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they face legal issues. This finding also applies to preferences regarding the amount donors donate. Respondents donated `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately-funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`. Respondents explained that they chose to give additional money to privately-funded human rights NGOs precisely because "the country limits non-profits."[^13685] The punishment mechanism found previously does not translate to the amount donated—while there is a decrease of `r md_dollar(abs(filter(amount, title == "Human rights | Government")$mu_diff))` in average donations to government-funded human rights NGOs facing crackdown, the chance this difference is less than zero is lower than our threshold (`r filter(amount, title == "Human rights | Government")$p_neq0`).

@@

This research note should be viewed as an exploratory study, and it raises numerous questions for future research. These include determining the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation, but preferences may not reflect actual behavior. Future research can also test the generalizability of our findings to other issue areas and other political contexts.

@@

[^supp]: See the online appendix for details about our sample demographics and balance across experimental conditions.

@@

[^mturk]: Samples from Mechanical Turk are not nationally representative and our sample skewed younger and more politically liberal. However, because we aimed our study at people who are willing to donate online, we are not overly concerned with these discrepancies. Moreover, a growing body of research comparing Mechanical Turk with other sampling services finds it generally comparable (see the online appendix for a lengthier discussion about this research).

>>>>

---
title: "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
  twitter: SuparnaChaudhry
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
  twitter: andrewheiss
date: "`r format(Sys.time(), '%B %e, %Y')`"
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: false
title-page: true
abstract: >-
  Government restrictions on NGOs have become increasingly pervasive across the globe. With reduced official aid and foundation funding available for NGOs, and an absence of philanthropic culture in many countries across the Global South, various NGOs are seeking funds from individual private donors in Western countries. How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making? While existing research has shown that donors rely on various heuristics from social networks and organization-level attributes, we argue that domestic political environments of NGO host countries can also serve as an important structural-level heuristic that can influence donor behavior. Using a survey experiment, we find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad. We discuss the implications of our results on the sustainability of organizations working in repressive countries.
thanks: >-
  We thank Mark Buntaine, Michael DeCrescenzo, Jeffrey Friedman, Thomas Leeper, and Tristan Mahr for their helpful comments and input. We also thank Samantha Camilletti and Joshua Dutro for their excellent research assistance. This experiment received approval by the human subjects research committees at both Christopher Newport University (018.042) and Brigham Young University (E18104). We preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at <https://osf.io/dx973/>.
author-note: >-
  Suparna Chaudhry, PhD, Assistant Professor of Political Science, Christopher Newport University; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University. 
additional-info: Figures should appear in color online only, not in print.
correspondence: >-
  Correspondence concerning this article should be addressed to Suparna Chaudhry, PhD, Department of Political Science, Christopher Newport University, Newport News, VA 23606, 757-594-7821. Contact: suparna.chaudhry@cnu.edu
word-count: "4,994"
keywords: international NGOs, donor behavior, philanthropy, human rights, repression
---

@@

Following the 2011 Egyptian uprising, just as domestic non-governmental organizations (NGOs) began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy. Egypt is not alone in this endeavor—India, Bolivia, Hungary, Russia, and others have also imposed funding restrictions on NGOs [@Carothers:2015; @DPR:2015]. Consequently, official aid flows and grants from large foundations to NGOs have considerably decreased in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].

In response to this shift in the NGO funding landscape, organizations have increasingly turned to *foreign* individual donors to offset the loss of governmental and foundation funding, [@BanksHulmeEdwards:2015] as funding from *domestic* donors in repressive countries is unreliable, inconsistent, and frequently prohibited. Citizens in the Global South often cannot support local NGOs, may prefer channeling funds to groups working on innocuous issues such as health and education over more contentious issues, or may be deterred by dismal tax incentives or a general fear of retribution [@DPR:2015; @RPC:2016; @Brechenmacher:2017]. NGOs have thus increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy. This amount is not insignificant—by 2016, total private giving to civil society organizations working in international affairs had increased to \$22.03 billion [@givingusa:2017].

In the face of increased crackdown on NGOs globally, how do individual donors in the U.S. feel about donating to legally besieged NGOs abroad? Do legal restrictions on NGOs influence donors' decision to donate? Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974]. While much of this research has focused on heuristics from social networks and organizational practices [@CrosonShang:2011; @Tremblay-BoirePrakash:2017], in this research note we argue that domestic political environments of NGO host countries can serve a structural heuristic that influences individual donor decisions. When donors are provided salient information about crackdown on NGOs and its impact on their activities, that information can serve as a heuristic of organizational deservingness, and consequently influence donor preferences and behavior. We use a survey experiment to measure the effect of crackdowns on stated donor preferences and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs. This effect persists when mediated by other organization-level heuristics like NGO issue area and its main funding sources.

@@

Below, we summarize existing research on the determinants of giving to NGOs and lay out our expectations regarding how crackdowns on NGOs may affect private philanthropy. We then describe our survey and present the results. We conclude with implications for NGOs working in repressive countries and lay out questions ripe for future research.

@@

Substantial research on charitable giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011], and more recently, the effect of social networks on philanthropy [@HerzogYang:2018]. However, research on individual donor behavior has overwhelming examined giving to local—rather than international—causes. While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore private philanthropy because individuals rely on signals and heuristics that may differ from the benchmarks used by large governmental and private donors.

The decision to donate to an NGO is rarely rational. In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017]. Existing research shows that information on the efficiency of NGOs merely steers rather than encourages or discourages overall donations [@ryazanov:efficiency]. Similarly, the effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010]. Instead, donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming. These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].

In addition to organizational factors that signal an NGO's trustworthiness and deservingness, we argue that structural factors—including whether an organization works abroad and the domestic political environment of the group's host country—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017]. We propose that the regulatory relationship between international NGOs (INGOs) and their host governments serves as a signal of NGO trustworthiness and deservingness. NGO legislation is not inherently restrictive, and governments frequently use laws to regulate the behavior of NGOs [@BloodgoodTB; @DeMattee:2018]. Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy. These stricter anti-NGO laws can signal to donors that governments perceive these groups as threatening and may crack down on them.

We argue that donors perceive legal crackdowns differently from organization-level heuristics—such as NGO missions, visions, values—because donors may be able to influence these latter attributes, at least to some extent. Conversely, donors can do little to change the domestic political environment of another country. Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged NGOs, even if donors are not completely satisfied with some organization-level features of a group. As such, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated.

@@

@fig:causal-path represents this relationship formally. Legal crackdowns (**C**) have a direct effect on donor decisions (**Y**; donation likelihood and amount) because of their heuristic function. Legal crackdowns do not occur in isolation, however. Countries are more likely to repress NGOs both when organizational issue areas (**I**) are in tension with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015]. Both of these organizational characteristics thus confound the causal effect of crackdowns on donor decisions and must be accounted for in the analysis—issue areas and funding sources simultaneously influence the likelihood of crackdown while also serving as organizational heuristics that influence donor perceptions of NGO deservingness.

@@

The final heuristic we examine is the *source of NGO funding*. Government grants to nonprofits can often crowd out private funding, though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991; @Heutel:2014]. Donors may feel less inclined to contribute to INGOs receiving funds from agencies like USAID because such funding can signal a lack of independence from the government. Organizations that receive substantial government funding frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012]. In contrast, individual donors who see that organizations are privately funded may feel that they can also contribute and help.

As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding again confounds the effect of anti-NGO crackdowns on donor behavior (see @fig:causal-path). Accordingly, the combination of legal crackdown and funding may reshape donor perceptions of deservingness. Individual donors may be less likely to donate to government-funded NGOs that face restrictions, since legal trouble with the organization's primary funder could fuel private donor mistrust (i.e. perhaps the NGO did something to deserve crackdown). Donors thus may be likely to donate more to NGOs that rely on private funding.

@@

To measure the effect of structural and organization-level heuristics on individual donor preferences, we use an experiment to vary the different signals donors are exposed to. Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for private individuals.

@@

We estimate the mean amount donated in each condition using a *t* distribution:

@@

These results give partial support to H~3a~. The source of funding has little influence on the preference to donate to humanitarian NGOs, but on average, donors are substantially more likely to want to give to privately-funded human rights NGOs than government-funded organizations. Additionally donors appear to both punish government-funded human rights NGOs facing crackdown and rally behind privately-funded NGOs facing those same hurdles. Respondents described their reasoning for the former as "[i]f the non-profit works in countries where non-profit activities are heavily restricted there's a good amount of waste and shortfalls in their activities and ability to assist others."[^3154467] Respondents also explained their motivation for increased support to privately funded NGOs as "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds.

@@

This trend also holds when accounting for NGO issue area. The crackdown condition elicits higher donations for both the human rights and humanitarian NGOs, though with varying levels of significance (see @fig:amount-diffs(B–C)). Emphasizing legal crackdown increases donations to human rights NGOs by `r md_dollar(filter(amount, title == "Human rights")$mu_diff)`, but with a lower probability of significance (`r filter(amount, title == "Human rights")$p_neq0`). In contrast, crackdowns boost donations to humanitarian NGOs by `r md_dollar(filter(amount, title == "Humanitarian assistance")$mu_diff)`, a `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` increase beyond the control condition (`r filter(amount, title == "Humanitarian assistance")$p_neq0`). We thus find support for H~2b~: donors give more to besieged humanitarian NGOs. We also find evidence for H~3b~. Donors give `r md_dollar(filter(amount, title == "Private")$mu_diff)` more (a `r percent_0(filter(amount, title == "Private")$pct_change)` increase) to legally besieged NGOs that are privately funded (`r filter(amount, title == "Private")$p_neq0`), while the crackdown condition has little effect on the amount donated to government-funded NGOs (`r filter(amount, title == "Government")$p_neq0`).

Combining issue areas and funding sources provides more texture. We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they face legal issues. This finding also applies to preferences regarding the amount donors donate. Respondents donated `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately-funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`. Respondents explained that they chose to give additional money to privately-funded human rights NGOs precisely because "the country limits non-profits."[^13685] The punishment mechanism found previously does not translate to the amount donated—while there is a decrease of `r md_dollar(abs(filter(amount, title == "Human rights | Government")$mu_diff))` in average donations to government-funded human rights NGOs facing crackdown, the chance this difference is less than zero is lower than our threshold (`r filter(amount, title == "Human rights | Government")$p_neq0`).

@@

This research note should be viewed as an exploratory study, and it raises numerous questions for future research. These include determining the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation, but preferences may not reflect actual behavior. Future research can also test the generalizability of our findings to other issue areas and political contexts.

@@

[^supp]: See the online appendix for the text of the survey, as well as details about our sample demographics and balance across experimental conditions.

@@

[^mturk]: Samples from Mechanical Turk are not nationally representative. However, because we targeted our study at people who are willing to donate online, we are not overly concerned with these discrepancies. Moreover, a growing body of research comparing Mechanical Turk with other sampling services finds it generally comparable—see the online appendix for a lengthier discussion about this research.
